A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 method.tex
Deleted commented out text that had been accidentally split onto multiple lines
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@652 ccdd05d5-56c1-461a-bf98-85f6876523b4

The detection procedure for just one set of intrinsic source parameters
$\theta$ starts by {\em whitening} the measurement data stream $x$.  This
involves finding a linear filter that renders the detector's noise \textsc{iid}
and Gaussian.  This filter is applied to the measurement, yielding the whitened
data stream $x^\mathrm W$.  The same linear filter is applied to the template
$h(\theta)$, yielding the whitened template $h^\mathrm W (\theta)$.  The
matched filter is the normalized cross-correlation of $h^\mathrm W$ and
$x^\mathrm W$, \editorial{After introducing the $\star$ notation for cross
correlation, must we define it for continuous and discrete time?}
%
$$
%
\rho(\theta) = \frac{h^\mathrm W (\theta) \star x^\mathrm W}{|h^\mathrm W
(\theta)|}.
%
$$
%
This is called the signal to noise ratio, or \textsc{snr}.  The detection
statistic is the modulus of this, $|\rho(\theta)|$, which has a $\chi^2$
distribution with 2 degrees of freedom in the absence of signal.%, and it
indicates the probability of a signal being present
\cite{wainstein:1962}\editorial{Comment about probability doesn't seem
relevant.}.

>>>>

The detection procedure for just one set of intrinsic source parameters
$\theta$ starts by {\em whitening} the measurement data stream $x$.  This
involves finding a linear filter that renders the detector's noise \textsc{iid}
and Gaussian.  This filter is applied to the measurement, yielding the whitened
data stream $x^\mathrm W$.  The same linear filter is applied to the template
$h(\theta)$, yielding the whitened template $h^\mathrm W (\theta)$.  The
matched filter is the normalized cross-correlation of $h^\mathrm W$ and
$x^\mathrm W$, \editorial{After introducing the $\star$ notation for cross
correlation, must we define it for continuous and discrete time?}
%
$$
%
\rho(\theta) = \frac{h^\mathrm W (\theta) \star x^\mathrm W}{|h^\mathrm W
(\theta)|}.
%
$$
%
This is called the signal to noise ratio, or \textsc{snr}.  The detection
statistic is the modulus of this, $|\rho(\theta)|$, which has a $\chi^2$
distribution with 2 degrees of freedom in the absence of signal.
